### 2012-03-27 doc/theses/mikula/analysis_of_xquery.tex
Master thesis: Corrections.

If there is a large enough set of XML documents available, it should be possible to correctly detect where to use \texttt{xs:sequence} and \texttt{xs:all} constructs \todo{Reference na Vostuv clanek}. However, if the inference is made using a smaller set of XML documents, it may happen that every occurrence of some element set is in the same order but the input data are not representative enough to be sure. Comparison of element order in queries can help to decide for the use of \texttt{xs:sequence}.

>>>>

If there is a large enough set of XML documents available, it should be possible to correctly detect where to use \texttt{xs:sequence} and \texttt{xs:all} constructs (paper \cite{Vosta:2008:EAC:1802514.1802522} deals with this problem). However, if the inference is made using a smaller set of XML documents, it may happen that every occurrence of some element set is in the same order but the input data are not representative enough to be sure. Comparison of element order in queries can help to decide for the use of \texttt{xs:sequence}.
